---
title: "Final"
author: "D54101039 Yu-Ting Chu"
date: January 5, 2024
header-includes:
   - \usepackage{bm, graphicx, fancyvrb, booktabs}
output: html_document
---

```{r set-options, echo=FALSE, cache=FALSE}
options(width=55)
knitr::opts_chunk$set(tidy.opts = list(width.cutoff = 45), tidy = TRUE)
```

# Problem 1

As part of a study on transportation safety, the U.S. Department of Transportation collected data on the number of fatal accidents per 1000 licenses and the percentage of licensed drivers under the age of 21 in a sample of 42 cities. Data collected over a one-year period follow. These data are contained in the file named Safety.


## Questions

1. Develop numerical and graphical summaries of the data.

2. Use regression analysis to investigate the relationship between the number of fatal
accidents and the percentage of drivers under the age of 21. For this estimated regression equation, perform an analysis of the residuals and discuss your findings and conclusions.

3. What conclusion and recommendations can you derive from your analysis?

```{r safety, tidy = TRUE, eval = TRUE, warning=FALSE,message=FALSE}
library(tidyverse)
library(readxl)
library(ggplot2)
safety = read_excel("C:/Users/朱郁庭/Desktop/safety.xlsx") 
head(safety)
```
1.
---
```{r safety1-1, tidy = TRUE, eval = TRUE, warning=FALSE,message=FALSE}
summary(safety)
```
"Percent Under 21":Minimum value is 8.00, maximum value is 18.00 and mean value is 12.26.

"Fatal Accidents per 1000":Minimum value is 0.039, maximum value is 4.100 and mean value is 1.922.

```{r safety1-2, tidy = TRUE, eval = TRUE, warning=FALSE,message=FALSE}
percent<-safety$"Percent Under 21"
fatal<-safety$"Fatal Accidents per 1000"
model <- lm(fatal ~ percent, safety)
plot(percent,fatal,
     xlab = "Percentage of Drivers Under 21", 
     ylab = "Fatal Accidents per 1000 Licenses",
     main = "Fatal Accidents vs Percentage of Drivers Under 21")
abline(model, col="blue")
```

According to the gragh, there is a positive relationship between the percentage of drivers under the age of 21 and the number of fatal accidents per 1000 licenses.

2.
---
```{r safety2-1, tidy = TRUE, eval = TRUE, warning=FALSE,message=FALSE}
summary(model)
```
In the regression report, when the percentage of drivers under the age of 21 increases by 1 unit, the number of fatal accidents per 1000 licenses will increase by 0.28705 unit. The p-value of the coefficient of the percentage of drivers under the age of 21 is less than 0.05, indicating that the percentage of drivers under the age of 21 is significant to the number of fatal accidents per 1000 licenses.

```{r safety2-2, tidy = TRUE, eval = TRUE, warning=FALSE,message=FALSE}
par(mfrow=c(1, 3))
resid <- resid(model)
plot(fitted(model), resid, main="residual vs. fitted value")
abline(0, 0)
qqnorm(resid)
qqline(resid)
plot(resid, main="residual")
```

The graph above is the diagnostic plots with the model. For the left plot, we draw the scatter for the fitted value and residuals to check if the residuals follow the assumption of constant variance. The plot shows that the residuals are mostly around 0, indicating that the residuals follow the assumption of constant variance, except for one observation that is far from 0.


For the middle plot, we check if the residuals follow normal distribution by qqplot. The plot shows that the residuals almost on the dotted line, indicating that the residuals follow the normal distribution, except for one observation that is far from the dotted line.


For the right plot, we draw the residuals to check if they are independent. The plot shows that the value of residuals are affected by the previous one, indicating that the residuals may not follow the assumption of independence.

3.
---
Conclusion:The observed relationship between the number of fatal accidents per 1000 licenses and the percentage of drivers under the age of 21 suggests a positive correlation. Specifically, as the percentage of young drivers increases, there appears to be a corresponding rise in the total number of fatal accidents. This linear association indicates that a higher proportion of young drivers might contribute to an increased occurrence of fatal accidents. 

Recommendation: Based on this analysis, it might involve targeted safety initiatives or educational programs aimed at young drivers. By focusing on this demographic and addressing factors contributing to accidents among younger drivers, it's possible to work toward reducing the overall number of fatal accidents. Moreover, stricter monitoring or additional safety measures for this age group could be explored to mitigate the risk of accidents on the road.

# Problem 2
Par, Inc., is a major manufacturer of golf equipment. Management believes that Par’s market share could be increased with the introduction of a cut-resistant, longer-lasting golf ball. Therefore, the research group at Par has been investigating a new golf ball coating designed to resist cuts and provide a more durable ball. The tests with the coating have been promising.
One of the researchers voiced concern about the effect of the new coating on driving distances. Par would like the new cut-resistant ball to offer driving distances comparable to those of the current-model golf ball. To compare the driving distances for the two balls, 40 balls of both the new and current models were subjected to distance tests. The testing was performed with a mechanical hitting machine so that any difference between the mean distances for the two models could be attributed to a difference in the two models. The results of the tests, with distances measured to the nearest yard, follow. These data are available on the website that accompanies the text.

## Questions
1. Formulate and present the rationale for a hypothesis test that Par could use to com- pare the driving distances of the current and new golf balls.
2. Analyze the data to provide the hypothesis testing conclusion. What is the p-value for your test? What is your recommendation for Par, Inc.?
3. Provide descriptive statistical summaries of the data for each model.
4. What is the 95% confidence interval for the population mean driving distance of
each model, and what is the 95% confidence interval for the difference between the
means of the two populations?
5. Do you see a need for larger sample sizes and more testing with the golf balls?Discuss.

```{r golf, tidy = TRUE, eval = TRUE, warning=FALSE,message=FALSE}
library(tidyverse)
library(readxl)
golf = read_excel("C:/Users/朱郁庭/Desktop/golf.xlsx") 
head(golf)
```
1.
---
$$
\mu_1 = population~mean~of~current
$$
$$
\mu_2 = population~mean~of~new
$$

$$
H_0: \mu_1-\mu_2 <= 0 
$$
$$
H_0: \mu_1-\mu_2 > 0
$$
Par's claim of improved quality due to the cut resistance in the new golf ball relies heavily on maintaining the same or improved driving distance compared to the current model. The hypotheses are designed such that rejecting the null hypothesis (H0) suggests that the new golf ball's mean driving distance is lower.

2.
---
```{r golf2, tidy = TRUE, eval = TRUE, warning=FALSE,message=FALSE}
t.test(golf$Current, golf$New,alternative ="greater")
```
The sample means for the current and new golf balls were 270.275 and 267.500, respectively. On average, the current golf ball showed a 2.775-yard advantage. , The p-value is 0.09399 at a significance level of 0.05, suggests that wedo not reject the null hypothesis (H0). Hence, there isn't enough statistical evidence to conclude that the new golf ball has a lower mean driving distance compared to the current one.

Therefore, Par, Inc. might consider further investigation or additional testing to confirm these findings. While the initial results don't decisively support the superiority of the new golf ball in terms of driving distance, continued examination with larger sample sizes or extended testing could provide a clearer understanding of the balls' comparative performance. This ongoing study would facilitate more informed decisions regarding the introduction of the new golf ball into the market.

3.
---
```{r golf3, tidy = TRUE, eval = TRUE, warning=FALSE,message=FALSE}
summary(golf$Current)
summary(golf$New)
```
"Current":Minimum value is 255.0, maximum value is 289.0 and mean value is 270.3.

"New":Minimum value is 250.0, maximum value is 289.0 and mean value is 267.5.

4.
---
```{r golf4, tidy = TRUE, eval = TRUE, warning=FALSE,message=FALSE}
t.test(golf$Current)
t.test(golf$New)  
t.test(golf$Current, golf$New)
```
The 95% confidence interval for the current model is [0267.4757,273.0743].

The 95% confidence interval for the new model is [264.3348,270.6652].

The 95% confidence interval for the difference between the means of the two populations is [-1.384937,6.934937].

5.
---
Expanding the sample size and conducting more tests on golf balls could indeed yield better results. Because H0 wasn't rejected, the research findings remain inconclusive. Despite the absence of evidence supporting the new golf ball's significantly lower mean driving distance, it's premature to assert that the mean distance for the new ball equals or surpasses the current ball's distance. This stance acknowledges the potential for a Type II error in this conclusion.

With a larger dataset, Par would gain a more comprehensive understanding of the differences in mean performance between the two golf balls. This enhanced data set would significantly contribute to refining the accuracy and reliability of the conclusions drawn from the study.


# Problem 3
The American Press Institute reports that almost 70% of all American adults use a computer to gain access to news. Based on generational differences, you suspect that the proportion of American adults under 30 years old who use a computer to gain access to news exceeds the proportion of Americans 30 years and older who use a computer to gain access to news. Data in the file ComputerNews represent responses to the question, “Do you use a computer to gain access to news?” given by random samples of American adults under 30 years old and Americans over 30 years old.

## Questions
1. Estimate the proportion of American adults under 30 years old who use a computer to gain access to news and the proportion of Americans over 30 years old who use a computer to gain access to news.
2. Provide a 95% confidence interval for the difference in proportions.
3. On the basis of your findings, does it appear the proportion of American adults
under 30 years old who use a computer to gain access to news exceeds the propor- tion of Americans over 30 years old who use a computer to gain access to news?

```{r computernews, tidy = TRUE, eval = TRUE, warning=FALSE,message=FALSE}
library(tidyverse)
library(readxl)
computernews = read_excel("C:/Users/朱郁庭/Desktop/computernews.xlsx") 
head(computernews)
```
1.
---
```{r computernews1, tidy = TRUE, eval = TRUE, warning=FALSE,message=FALSE}
table(computernews$"Under 30" == "Yes")
prop.table(table(computernews$"Under 30" == "Yes"))
table(computernews$"30 and Older" == "Yes")
prop.table(table(computernews$"30 and Older" == "Yes"))
```
The proportion of American under 30 years old who use a computer to gain access to news: 0.7266667 

The proportion of Americans over 30 years old who use a computer to gain access to news: 0.545 

2.
---
```{r computernews2, tidy = TRUE, eval = TRUE, warning=FALSE,message=FALSE}
prop_under30<-109/150
prop_over30<-109/200
prop_diff <- prop_under30 - prop_over30
prop_se <- sqrt((prop_under30 * (1 - prop_under30)) / 150 + (prop_over30 * (1 - prop_over30)) / 200)
margin_error <- qnorm(0.975) * prop_se
prop_diff - margin_error
prop_diff + margin_error
```
The 95% confidence interval for the difference in proportions is [0.08242157,0.2809118]

3.
---
The 95% confidence interval doesn"t include 0 and both values are positive. Conclude that the proportion of American adults under 30 years old who use a computer to gain access to news is greater than the proportion of Americans over 30 years old that use a computer to gain access to news.